IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2010-01-15 doc/msc-proposal/msc-routing.tex
proposal: routing

\subsection{RPL Model}
Each DAG instance constructs a routing topology optimized for a certain OF. Traffic that belongs to a specific DODAG Instance is marked in the flow label of the IPv6 header. A network may have more than one DAG Instance which operate independently. Applications may tag traffic to follow an appropriate DAG instance, i.e., optimized for low latency or low energy.

@@

\subsection{Messages}

>>>>

\subsection{Model}
Each DAG instance constructs a routing topology optimized for a certain OF. Traffic that belongs to a specific DODAG Instance is marked in the flow label of the IPv6 header. A network may have more than one DAG Instance which operate independently. Applications may tag traffic to follow an appropriate DAG instance, i.e., optimized for low latency or low energy.

@@

\subsection{Messages}
The draft \cite{draft-rpl-04} defines the RPL Control Message, which is a new ICMPv6 message. The format of this message is shown in Figure \ref{fig:rpl.control.message}.
\begin{figure}[htp]
\begin{mylisting}
\begin{verbatim}
   0                   1                   2                   3
   0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1
   +-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
   |     Type      |     Code      |          Checksum             |
   +-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
   |                                                               |
   +                         Message Body                          +
   |                                                               |
\end{verbatim}
\end{mylisting}
\caption{RPL Control Message}\label{fig:rpl.control.message}
\end{figure}

The Type for the RPL Control message has the value of 155. The Code identifies the RPL Control Messages as follows:  0x01 -- DAG Information Solicitation; 0x02: DAG Information Object; 0x04: Destination Advertisement Object. The DAG Information Solicitation (DIS) message is used to solicit a DAG Information Object from a RPL node. The DAG Information Object carries a number of metrics and other information that allows a node to discover a DAG Instance, select its DAG parents, and avoid loops. The Destination Advertisement Object (DAO) is used to propagate destination information upwards along the DODAG. The format of these messages is specified in the internet draft \cite{draft-rpl-04}.
